A thesis draft

### 2018-10-11 draft.tex
Use Emacs formatting
Add footnote
Add part about MANO, add papers to read before adding new content

 Through the history of internet, many factor changed and new innovations came,
but at the end of the day a foundamental key remained: TCP/IP performance are, 
indeed, what the users unconsciously want.\todo{Idea: talk about how TCP/IP 
performes quite well in wired connections, while in wireless one, such as 
wireless/satellite, sucks ass} In this context network optimization plays an 
important role, and it is for this reason that network packets are processed 
while traversing the network in order to make their transmission as fast as 
possible. On top of that, mobile traffic is continuously surging every year, 
with the backbones having more and more data to process. In this context, 
in-hardware VNF solutions are becoming less efficent. Their time-to-deploy, in 
fact, is very high compared to the requirements of the network. With this 
trend, in-hardware solutions will not be able to keep up. Is with this 
considerations that software solutions are being proposed to become the new way 
to deploy network components. While less efficent, they are faster to bring them 
up, offering an unprecedented flexibility\footnote{SDN/NFV-Based Mobile Packet 
Core Network Architectures: A Survey}. Furthermore, new virtualization 
technologies such as Cloud computing and Docker are becoming more and more 
mature for being employed in large-scale production environments, where new 
frameworks, called orchestrators (e.g. Kubernetes, Docker Swarm), allow to 
easily manage the application lifecyle, i.e. deployment, scale up/down
and finally, removal.

@@

The analysis of this topic revealed to be trivial: since internet has many
different protocols that would become infeasible to support all of them at the
same time, packet incapsulation present itself as the only faseable solution:
every packet incoming in the VNFs has already been incapsulated by the MANO,
\todo{Not sure about this, please give it a check - Not sure but I think that
it is not part of the MANO the encapsulation of the packets. Also I think that
the main purpose of UDP encapsulation is not to hide the protocol used on the
edges but 1) usa a ``quick protocol to exchange data among VNFs and 2) we are
hiding the path not the protocol itself. As we were discussing, we are creating
some sort of proxy, so the aim will be the same even if we support a plethora
of protocols.''} making the whole architecture indipendent from the protocol a
particolar flux of data uses. To achieve this, TUN/TAP
\todo{Find out acronym - EPKT? (Encapsulated PacKeT)}
interfaces were used to deploy a tunnel between VNFs, allowing them to pass
packets encapsulated in UDP ones.

@@

\item \textbf{VNFs} this are the core components that perform packets
  manipulation. This components are design to be lightweight services able to
  elaborate a great amount of packets per seconds. Manupulation can be of two
  typologies: stateful or stateless. In the first case, a state is maintained,
  and the VNF can perform heuristics about data coming through it (especially
  useful to detect patterns in the data flow, e.g. DDos attacks). In the second
  case, no state is maintained, and every packet is treated without any
  particular assumption. \todo{Add ref to chap about SFC?}

\item \textbf{NFV Management and Orchestration (MANO)} also known as NFV
  Orchestrator (NFVO) is responsible for the end-to-end management and
  orchestration of network services (NS), also called SFC. The MANO has
  different responsabilities, such as managing the
  istantiation/destruction/modification of the SFCs, that achieves interacting
  with the VIM. \todo{Expand this part}

>>>>

 Through the history of internet, many factor changed and new innovations came,
 but at the end of the day a foundamental key remained: TCP/IP performance are,
 indeed, what the users unconsciously want.\todo{Idea: talk about how TCP/IP
   performes quite well in wired connections, while in wireless one, such as
   wireless/satellite, sucks ass} In this context network optimization plays an
 important role, and it is for this reason that network packets are processed
 while traversing the network in order to make their transmission as fast as
 possible. On top of that, mobile traffic is continuously surging every year,
 with the backbones having more and more data to process. In this context,
 in-hardware VNF solutions are becoming less efficent. Their time-to-deploy, in
 fact, is very high compared to the requirements of the network. With this
 trend, in-hardware solutions will not be able to keep up. Is with this
 considerations that software solutions are being proposed to become the new way
 to deploy network components. While less efficent, they are faster to bring
 them up, offering an unprecedented flexibility\todo{CITE: SDN/NFV-Based Mobile
   Packet Core Network Architectures: A Survey}. Furthermore, new virtualization
 technologies such as Cloud computing and Docker are becoming more and more
 mature for being employed in large-scale production environments, where new
 frameworks, called orchestrators (e.g. Kubernetes, Docker Swarm), allow to
 easily manage the application lifecyle, i.e. deployment, scale up/down and
 finally, removal.

@@

The analysis of this topic revealed to be trivial: since internet has many
different protocols that would become infeasible to support all of them at the
same time, packet incapsulation present itself as the only faseable solution:
every packet incoming in the VNFs has already been encapsulated by the MANO,
\todo{Not sure about this, please give it a check - Not sure but I think that it
  is not part of the MANO the encapsulation of the packets. Also I think that
  the main purpose of UDP encapsulation is not to hide the protocol used on the
  edges but 1) usa a ``quick protocol to exchange data among VNFs and 2) we are
  hiding the path not the protocol itself. As we were discussing, we are
  creating some sort of proxy, so the aim will be the same even if we support a
  plethora of protocols.''} making the whole architecture indipendent from the
protocol a particolar flux of data uses. To achieve this, TUN/TAP interfaces 
were used to deploy a tunnel between VNFs, allowing them to pass packets 
encapsulated in UDP ones.

@@

\item \textbf{VNFs} this are the core components that perform packets
  manipulation. This components are design to be lightweight services able to
  elaborate a great amount of packets per seconds. Manupulation can be of two
  typologies: stateful or stateless. In the first case, a state is maintained,
  and the VNF can perform heuristics about data coming through it (especially
  useful to detect patterns in the data flow, e.g. DDos attacks). In the second
  case, no state is maintained, and every packet is treated without any
  particular assumption. Following the RFC 7665, the VNF are also called Service
  Function (SF)\footnote{From now on the two terminologies will be use in a
    interchangeable way.}. \todo{Add ref to chap about SFC?}

\item \textbf{NFV Management and Orchestration (MANO)} also known as NFV
  Orchestrator (NFVO) is responsible for the end-to-end management and
  orchestration of network services (NS), also called SFC. The MANO has
  different responsabilities, such as managing the
  istantiation/destruction/modification of the SFCs, that achieves interacting
  with the VIM.\todo{CITE: SDN/NFV-Based Mobile Packet Core Network
Architectures: A Survey}. Finally, the mano can integrate with 
Operational and Business Support Systems (OSS/BSS), \todo{Expand this part with 
the following papers: https://www.tandfonline.com/doi/abs/10.1057/jors.1995.176 
https://ieeexplore.ieee.org/abstract/document/6963800 
https://www.computer.org/csdl/proceedings/ifcsta/2009/3930/01/3930a466-abs.html}
